\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-09-05 doc/manuscript.tex
Added concept figure to Intro

\author[1]{Peter B. Adler}  %\thanks{Corresponding author. Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah Email: peter.adler@usu.edu}}
\author[2]{Ethan White}
\author[1]{Michael Cortez?}
\author[3]{Heather Lynch?}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{some shitty Florida joint}

@@

>>>>

\author[1]{Peter B. Adler}  %\thanks{Corresponding author. Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah Email: peter.adler@usu.edu}}
\author[2]{Ethan White}
\author[3]{Michael Cortez}
\affil[1]{Department of Wildland Resources and the Ecology Center, Utah State University, Logan, Utah}
\affil[2]{some shitty Florida joint}
\affil[3]{some shitty Florida joint}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=0.5 \textwidth] {fast-slow-figure.png}
	\caption{Fast and slow processes operate at different time scales, and are reflected in different kinds of datasets. Fast processes, such as births, deaths, and individual growth, operate at all time scales, but are the exclusive drivers of the short-term dynamics captured in most time series datasets. Slower processes, such as evolutionary selection on genotype frequencies, ecological selection on species abundances, and colonization and extinction, interact with fast processes to drive dynamics over the long-term. The influence of these slow processes is seen in very long time series, or in spatial gradients. Spatiotemporal datasets with long enough records to capture changes in spatial patterns are rare, but would be extremely valuable for understanding dynamics at intermediate time scales. The time scales shown here were chosen with vascular plants in mind; the same concepts would apply for much shorter-lived organisms but at shorter time scales.   }
	\label{fig:fast-slow-concept}
\end{figure}
